### 2018-12-10 paper/paper.tex
Add a couple paragraphs. Some small corrections.

            We also examined the effect of tuning the number of feature words chosen by the TF-IDF 
            extractor. The number of feature words chosen for initial analysis was 50, but subsequent 
            tests ranged from 50 to 1050 in steps of 200.
        \section{Results}
            Classifiers were evaluated on precision and recall on the spam class. Overall, precision is
            weighted more heavily than recall in the evaluation because it would likely be more disruptive 
            to classify a ham email as spam than to let a spam message slip through.
            \subsection{General Precision and Recall}
                Overall, the classifiers performed well with just features extracted from the email body.
                Precision and recall comparison can be found in \autoref{fig:precision_recall} with direct 
                number comparison in \autoref{tab:precision_recall}.

                \begin{Figure}
                    \begin{tabular}{|l|l|l|}
                    \hline
                                  & Precision & Recall \\ \hline
                    KNN           & 90.91     & 51.02  \\ \hline
                    Naive Bayes   & 83.67     & 83.67  \\ \hline
                    Random Forest & 98.84     & 86.73  \\ \hline
                    SVM           & 83.33     & 40.82  \\ \hline
                    \end{tabular}
                    \captionof{table}{Precison and Recall}
                    \label{tab:precision_recall}
                \end{Figure}

@@

@@

        %\section{Classifier Selection}

@@

        %\section{Conclusion}

        %\section{References}
        % \printbibliography
        \section{Conclusion}

            This paper has shown that the usage of machine learning alone can preform
            the classification well, compared to other's results our metrics are lower
            than the other paper's we are comparing ourselves against. Adding more features
            that aren't word based may help even more with performance and also increasing the
            size of the dataset would help as well. We also recognize the limitations of
            this implementation lends itself to only classify emails from the early 2000s, as
            we did no testing on modern email data which may have a distribution that doesn't
            work well with our implementation.
        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}

>>>>

            We also examined the effect of tuning the number of feature words chosen by the TF-IDF 
            extractor. The number of feature words chosen for initial analysis was 50, but subsequent 
            tests ranged from 50 to 1050 in steps of 200.
        \section{Results}
            Classifiers were evaluated on precision and recall on the spam class. Overall, precision is
            weighted more heavily than recall in the evaluation because it would likely be more disruptive 
            to classify a ham email as spam than to let in an occasional spam message. Subsequently, the 
            classifiers were also subjected to various feature word counts to observe the effect.
            \subsection{General Precision and Recall}
                Overall, the classifiers performed well with just features extracted from the email body.
                Precision and recall comparison can be found in \autoref{fig:precision_recall} with direct 
                number comparison in \autoref{tab:precision_recall}.

                \begin{Figure}
                    \begin{tabular}{|l|l|l|}
                        \hline
                        & Precision & Recall \\ \hline
                        KNN                                 & 90.91     & 51.02  \\ \hline
                        Naive Bayes                         & 83.67     & 83.67  \\ \hline
                        Random Forest                       & 98.84     & 86.73  \\ \hline
                        SVM                                 & 83.33     & 40.82  \\ \hline
                        Naive Bayes \cite{hovold2005naive}  & 98.46     & 99.66  \\ \hline
                        DBM \cite{tzortzis2007deep}         & 96.40     & 95.51  \\ \hline
                        SVM \cite{tzortzis2007deep}         & 96.14     & 95.24  \\ \hline
                    \end{tabular}
                    \captionof{table}{Precison and Recall}
                    \label{tab:precision_recall}
                \end{Figure}

@@

                Comparing with classifiers by other researchers in \autoref{tab:precision_recall}, the 
                Random Forest classifier performs better in precision than all three classifiers by other researchers. 
                Looking at recall, however, leaves much to be desired. Likely due to focusing solely on email body 
                content for text analysis, our implementation misses important information in subject lines or 
                email addresses.

@@

@@

        \section{Conclusion}

            This paper has shown that the usage of machine learning alone on email body text 
            along with a few other features can preform the classification well. 
            However, our metrics are lower
            than the other papers we are comparing against ourselves. Adding more features
            that aren't word based may help even more with performance and also increasing the
            size of the dataset would help as well. We also recognize the limitations of
            this implementation lending itself to only classify emails from the early 2000s, as
            we did no testing on modern email data which may have a distribution that doesn't
            work well with our implementation.
        \nocite{*}
        \bibliography{paper} 
        \bibliographystyle{alpha}
    \end{multicols}
\end{document}
